---
title: "Running Abimo"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Running Abimo}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

This vignette aims at demonstrating how to work with the kwb.abimo package.

## Basic model run

```{r basic-run}
result <- kwb.abimo::run_abimo(input_data = kwb.abimo::abimo_input_2019)

head(result)
```

## Load and modify input data

```{r}
input_data <- kwb.abimo::abimo_input_2019

# Have a look at the column types. IMPORTANT: Modifications must not change the
# types!
str(input_data)

# Assigning a value of e.g. 600 to an integer column converts the column
# type to double (floating point)!

typeof(input_data$REGENJA) # integer

input_data$REGENJA <- 600

# run_abimo() will complain now...
#kwb.abimo::run_abimo(input_data = input_data)
# Error: Column 'REGENJA' does not have the expected type (integer)!

# Really?
typeof(input_data$REGENJA) # now double

# Problem: By assigning 600, the type was implicitly converted to double.
# Use "L" to indicate integer values (or use as.integer())
input_data$REGENJA <- 600L

# Or e.g.
input_data$REGENJA <- as.integer(1.05 * kwb.abimo::abimo_input_2019$REGENJA)

typeof(input_data$REGENJA) # now integer (again)
```

## Run Abimo with the modified data

```{r}
result <- kwb.abimo::run_abimo(input_data = input_data)

head(result)
```

## Load and modify a configuration (config.xml)

```{r}
# Create a configurator object (from default config.xml stored in this package)
config <- kwb.abimo::create_configurator()

# Provide xpath expressions as a means of addressing the single config elements
xpaths <- kwb.abimo::get_xpaths()

# Get/set Infiltrationsfaktoren using the xpath expressions...
xp <- xpaths$Infiltrationsfaktoren

config$get(xp$Dachflaechen)
config$set(xp$Dachflaechen, 0.6)
config$get(xp$Dachflaechen) # check the change

config$get(xp$Belaglsklasse1)
config$set(xp$Belaglsklasse1, 0.99)
config$get(xp$Belaglsklasse1) # check the change

# Get/set Bagrovwerte ...
xp <- xpaths$Bagrovwerte
# ...

# Get/set ErgebnisNachkommaStellen...
xp <- xpaths$ErgebnisNachkommaStellen
# ...

# Get/set Diverse ...
xp <- xpaths$Diverse
config$get(xp$BERtoZero)
config$set(xp$BERtoZero, "true")

config$get(xp$NIEDKORRF)
config$set(xp$NIEDKORRF, 1.23)

# Check the changes
config$get(xp$BERtoZero)
config$get(xp$NIEDKORRF)

# More complicated: variable node sets

# Modify existing nodes
xp <- xpaths$PotentielleVerdunstung
config$get_nodes(xp)
config$modify_node(xp, i = 1L, bezirke = "123-125", etp = 123, etps = 234)
config$modify_node(xp, 6, etp = "666")
config$get_nodes(xp) # check the changes

xp <- xpaths$PotentielleVerdunstung
config$get_nodes(xp)
#config$modify_node(xp, ...)

# TODO: Add/remove nodes
```

## Run Abimo with the modified configuration

```{r run-with-config}
result <- kwb.abimo::run_abimo(
  input_data = kwb.abimo::abimo_input_2019,
  config = config
)

head(result)
```

Internally, a new `config_<date-time-string>.xml` file was created in the
temporary folder:

```{r dir-tempdir}
dir(tempdir())
```

## Manually save configuration object to XML

You may create your own config files from config objects using `save()`:

```{r save-config}
new_xml_file <- config$save(name = "config_tmp.xml")
```

If something goes wrong, you may compare the created xml file with the
original file, e.g. using TortoiseSVN->Diff...

```{r open-tempdir}
# Open the folder containing the xml file
kwb.utils::hsOpenWindowsExplorer(dirname(new_xml_file))
```
